The SMT Competition 2015--2018

### 2019-08-27 2018/report/SMT-COMP.tex
Moving the scoring explanation

@@

@@

Solvers in each division (of each track) are ranked according to a
metric that is based, first, on the number of erroneous responses
(which is usually~0, but solvers that did give erroneous responses are
ranked below solvers that did not); second, on the number of correct
responses; third, on the wall-clock and CPU time that the solver
process consumed.  For the \ucoretrack (which uses unsatisfiable
benchmarks only), the reduction in the size of the unsatisfiable core
is used instead of the number of correct responses.  A detailed
description of the scoring can be found in the competition
rules~\cite{rules18}.

@@

The competition-wide ranking for the \maintrack was retained and
refined after~2014.  Table~\ref{table:competition-wide-ranking} shows
the best three solvers according to this ranking for 2015--2018.  Also
shown is Z3, which ranked in high position each year but was running
hors concours.  Sequential and parallel performance are reported
separately.
%
Note that scores are not directly comparable between different years:
the set of benchmarks changes from one year to the other, and also the
formula to compute the score changed (see below).  Moreover, readers
should keep in mind that this ranking---like any method that maps the
performance of solvers for a broad range of logics to a
one-dimensional value---is inherently limited.  We refer to the
individual division rankings (Section~\ref{sec:division-rankings}) for
more detailed information about each solver.

>>>>

\subsection{Division Rankings}
\label{sec:scoring-division-rankings}

Solvers in each division (of each track) are ranked according to a
metric that is based, first, on the number of erroneous responses
(which is usually~0, but solvers that did give erroneous responses are
ranked below solvers that did not); second, on the number of correct
responses; third and fourth, on the wall-clock and CPU time,
respectively, that the solver process consumed.  For the \ucoretrack
(which uses unsatisfiable benchmarks only), the reduction in the size
of the unsatisfiable core is used instead of the number of correct
responses.  A detailed description of the scoring can be found in the
competition rules~\cite{rules18}.

@@

\subsection{Competition-Wide Ranking}
\label{sec:scoring:floc}

The competition-wide ranking for the \maintrack was retained and
refined after~2014.  Table~\ref{table:competition-wide-ranking} shows
the best three solvers according to this ranking for 2015--2018.  Also
shown is Z3, which ranked in high position each year but was running
hors concours.  Sequential and parallel performance are reported
separately.

@@

@@

Table~\ref{table:competition-wide-ranking} shows the best three
solvers according to the competition-wide ranking for 2015--2018.
Also shown is Z3, which ranked in high position each year but was
running hors concours.  Sequential and parallel performance are
reported separately.
%
Note that scores are not directly comparable between different years:
the set of benchmarks changes from one year to the other, and also the
formula to compute the score changed (see below).  Moreover, readers
should keep in mind that this ranking---like any method that maps the
performance of solvers for a broad range of logics to a
one-dimensional value---is inherently limited.  We refer to the
individual division rankings (Section~\ref{sec:division-rankings}) for
more detailed information about each solver.
